### 2021-08-03 README.Rmd
CRAN checks pass

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex %>% 
      mutate(sp = to_any_case(sp)),
    census_2 = census_2_ex %>% 
      filter(!str_detect(codes, "R")) %>% 
      mutate(sp = to_any_case(sp)),
    id = "ID"
  )
```

@@

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_ex, id = "ID")
focal_vs_comp_ex
```

>>>>

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex %>% 
      mutate(sp = to_any_case(sp)),
    census_2 = census_2_ex %>% 
      filter(!str_detect(codes, "R")) %>% 
      mutate(sp = to_any_case(sp)),
    id = "ID"
  ) %>% 
  # Compute basal area:
  mutate(basal_area = 0.0001 * pi * (dbh1 / 2)^2)
```

@@

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_ex, id = "ID", comp_x_var = "basal_area")
focal_vs_comp_ex
```
